Automating Political Bias Prediction

### 2016-03-31 manuscript/political_bias_prediction.tex
More tables and some text.

\setcounter{tocdepth}{3}
\usepackage{graphicx}
% For citations
\usepackage{natbib}
\usepackage{amsmath,amsfonts,amscd,amssymb}
\usepackage{dsfont}
\renewcommand{\vec}[1]{\mathbf{#1}}
\usepackage{hyperref}
\DeclareMathOperator*{\argmax}{argmax}
\DeclareMathOperator*{\argmin}{argmin}
\DeclareMathOperator*{\Corr}{Corr}
\newcommand{\R}{\mathds{R}}

\usepackage{url}
\urldef{\mailsa}\path|{felix.biessmann,|
\newcommand{\keywords}[1]{\par\addvspace\baselineskip
\noindent\keywordname\enspace\ignorespaces#1}

@@

% Confusion matrix
%\begin{table}[t]\label{tab:conf_mat_four_class}
%\begin{center}
%\begin{tabular}{lrrrr}
%&	1402&518&216&179\\
%&510&1939&295&306\\
%&185&235&1422&766\\
%&202&271&672&2692\\
%\end{tabular}
%\end{center}
%\end{table}

\begin{table}[t]
\begin{center}
\begin{tabular}{lrrrrrrrr}
& \multicolumn{4}{c}{\bf Held-out parliament speeches} & \multicolumn{4}{c}{\bf Party Manifestos}\\
    &         precision    &recall &  f1-score  & N    &         precision    &recall &  f1-score  & N\\
\hline \hline
       cducsu   &    0.62  &    0.81  &    0.70  &     706&0.26    &  0.58   &   0.36    &  2030\\
        fdp    &   0.70   &   0.37  &    0.49    &   331&0.38   &   0.28    &  0.33   &   2319\\
     gruene &      0.59  &    0.40   &   0.48   &    298&0.47  &    0.20   &   0.28 &     3747\\
      linke    &   0.71   &   0.61  &    0.65    &   338&0.30   &   0.47   &   0.37    &  1701\\
        spd   &    0.60   &   0.69  &    0.65   &    606&0.26   &   0.16   &   0.20  &    2278\\
\hline
avg / total &      0.64   &   0.63   &   0.62    &  2279 &0.35    &  0.31 &     0.30   &  12075
%
\end{tabular}
\end{center}
\caption{
\label{tab:results_four_classes}
Classification performance on the party affiliation prediction problem for data from the 17th legislative period on test set and evaluation set, respectively. Chance level is at 0.2.  
}
\end{table}

\begin{table}[t]
\begin{center}
\begin{tabular}{lrrrrrrrr}
& \multicolumn{4}{c}{\bf Held-out parliament speeches} & \multicolumn{4}{c}{\bf Party Manifestos}\\
    &         precision    &recall &  f1-score  & N    &         precision    &recall &  f1-score  & N\\
\hline \hline
government    &   0.83   &   0.84&      0.84     & 1037 & 0.49  &    0.59 &     0.54  &    4349\\
 opposition     &  0.86  &    0.86   &   0.86    &  1242 & 0.74 &     0.66  &    0.70   &   7726\\
\hline
avg / total   &    0.85 &     0.85 &     0.85  &    2279 & 0.65  &     0.63  &     0.64  &    12075\\

%
\end{tabular}
\end{center}
\caption{
\label{tab:results_binary}
Classification performance on the binary prediction problem in the 17th legislative period, categorizing speeches to government (FDP/CDU/CSU) and opposition (Linke, Gr\"une, SPD).
}
\end{table}

>>>>

\setcounter{tocdepth}{3}
\usepackage{graphicx}
% For citations
\usepackage{natbib}
\usepackage{amsmath,amsfonts,amscd,amssymb}
\usepackage{dsfont}
\renewcommand{\vec}[1]{\mathbf{#1}}
\usepackage{hyperref}
\DeclareMathOperator*{\argmax}{argmax}
\DeclareMathOperator*{\argmin}{argmin}
\DeclareMathOperator*{\Corr}{Corr}
\newcommand{\R}{\mathds{R}}
\usepackage{multicol}
\usepackage{multirow}
\usepackage{pbox}
\usepackage{url}
\urldef{\mailsa}\path|{felix.biessmann,|
\newcommand{\keywords}[1]{\par\addvspace\baselineskip
\noindent\keywordname\enspace\ignorespaces#1}

@@

% Confusion matrix
\begin{table}[t]\label{tab:conf_mat_four_class}
\begin{tabular}{lccccccc}
&&& \multicolumn{5}{c}{Predicted Class}\\
&&& cducsu & fdp& gruene& linke& spd\\
\multirow{5}{*}{\rotatebox{90}{\pbox{3cm}{\centering True Class}}}& &cducsu &1186 &289& 178& 198& 179\\
&&fdp &882& 658& 236& 329& 214\\
&&gruene &1174& 404& 764& 941& 464\\
&&linke &388& 92& 214& 806& 201\\
&&spd &999& 268& 240& 398& 373\\
 \multicolumn{8}{c}{\bf 17th Bundestag}\\
\end{tabular}
\quad
\begin{tabular}{lcccccc}
&&& \multicolumn{4}{c}{Predicted Class}\\
&&& cducsu & gruene& linke& spd\\
\multirow{4}{*}{\rotatebox{90}{\pbox{3cm}{\centering True Class}}}&&cducsu&1912& 156& 331& 584\\
&&gruene&2092& 827& 1311& 1444\\
&&linke&596& 186& 1216& 557\\
&&spd&1284& 226& 563& 916\\
 \multicolumn{7}{c}{\bf 18th Bundestag}\\
\end{tabular}
\caption{\label{tab:confusion} Confusion matrices for predictions on evaluation data (party manifestos) for classifiers trained on parliament speeches for the 17th legislative period (left) and 18th legislative period (right); the most prominent effect is the high likelihood for a party to be taken as the strongest, governing party, cdu/csu. In particular the green party suffers from this effect: when trained on the speeches in the 18th Bundestag, 2092 statements out of the green party's manifesto were classified as belonging to the cducsu party. This can be interpreted as a change in policies of the conservative party cdu/csu towards the policies of the green party.}
\end{table}

\begin{table}[t]
\begin{center}
\begin{tabular}{lcccccccc}
& \multicolumn{4}{c}{\bf Held-out parliament speeches} & \multicolumn{4}{c}{\bf Party Manifestos}\\
    &         precision    &recall &  f1-score  & N    &         precision    &recall &  f1-score  & N\\
\hline \hline
       cducsu   &    0.62  &    0.81  &    0.70  &     706&0.26    &  0.58   &   0.36    &  2030\\
        fdp    &   0.70   &   0.37  &    0.49    &   331&0.38   &   0.28    &  0.33   &   2319\\
     gruene &      0.59  &    0.40   &   0.48   &    298&0.47  &    0.20   &   0.28 &     3747\\
      linke    &   0.71   &   0.61  &    0.65    &   338&0.30   &   0.47   &   0.37    &  1701\\
        spd   &    0.60   &   0.69  &    0.65   &    606&0.26   &   0.16   &   0.20  &    2278\\
\hline
avg / total &      0.64   &   0.63   &   0.62    &  2279 &0.35    &  0.31 &     0.30   &  12075
%
\end{tabular}
\end{center}
\caption{
\label{tab:results_17}
Classification performance on the party affiliation prediction problem for data from the 17th legislative period on test set and evaluation set, respectively. Chance level is at 0.2.  
}
\end{table}

\begin{table}[t]
\begin{center}
\begin{tabular}{lcccccccc}
& \multicolumn{4}{c}{\bf Held-out parliament speeches} & \multicolumn{4}{c}{\bf Party Manifestos}\\
    &         precision    &recall &  f1-score  & N    &         precision    &recall &  f1-score  & N\\
\hline \hline
    cducsu    &   0.66   &   0.82   &   0.73    &   456 & 0.32  &    0.64  &    0.43    &  2983\\
     gruene   &    0.68    &  0.54   &   0.60    &   173   &0.59   &   0.15   &   0.23   &   5674\\
      linke     &  0.77  &    0.58    &  0.66    &   173 & 0.36   &   0.48   &   0.41   &   2555\\
        spd     &  0.60  &    0.54   &   0.57    &   330 & 0.26 &     0.31   &   0.28     & 2989\\
\hline
avg / total    &   0.66  &    0.66  &    0.65   &   1132&  0.42 &     0.34  &    0.32&     14201\\
%
\end{tabular}
\end{center}
\caption{
\label{tab:results_18}
Classification performance on the party affiliation prediction problem for data from the 18th legislative period on test set and evaluation set, respectively. 
}
\end{table}

\begin{table}[t]
\begin{center}
\begin{tabular}{lcccccccc}
& \multicolumn{4}{c}{\bf Held-out parliament speeches} & \multicolumn{4}{c}{\bf Party Manifestos}\\
    &         precision    &recall &  f1-score  & N    &         precision    &recall &  f1-score  & N\\
\hline \hline
government    &   0.83   &   0.84&      0.84     & 1037 & 0.49  &    0.59 &     0.54  &    4349\\
 opposition     &  0.86  &    0.86   &   0.86    &  1242 & 0.74 &     0.66  &    0.70   &   7726\\
\hline
avg / total   &    0.85 &     0.85 &     0.85  &    2279 & 0.65  &     0.63  &     0.64  &    12075\\

%
\end{tabular}
\end{center}
\caption{
\label{tab:results_binary_17}
Classification performance on the binary prediction problem in the 17th legislative period, categorizing speeches into government (FDP/CDU/CSU) and opposition (Linke, Gr\"une, SPD).
}
\end{table}

\begin{table}[t]
\begin{center}
\begin{tabular}{lcccccccc}
& \multicolumn{4}{c}{\bf Held-out parliament speeches} & \multicolumn{4}{c}{\bf Party Manifestos}\\
    &         precision    &recall &  f1-score  & N    &         precision    &recall &  f1-score  & N\\
\hline \hline
government   &    0.88  &    0.95    &  0.92   &    786   &0.52   &   0.66 &     0.58  &    5972\\
 opposition    &   0.86    &  0.71   &   0.78   &    346 & 0.69  &    0.56    &  0.62   &   8229\\
\hline
avg / total    &   0.88    &  0.88     & 0.87  &    1132 &  0.62   &   0.60    &  0.60 &    14201\\
%
\end{tabular}
\end{center}
\caption{
\label{tab:results_binary_18}
Classification performance on the binary prediction problem in the 18th legislative period, categorizing speeches into government (SDP/CDU/CSU) and opposition (Linke, Gr\"une).
}
\end{table}
